\sysfull

### 2018-08-05 paper/asplos19/paging.tex
partial commit paging

\sys's {\em virtual memory manager} (VMM) abstracts the physical address space of the non-volatile memory (FRAM) and divides it into \emph{private} and \emph{shadow} buffers. Each buffer is divided into pages. The VMM prohibits applications from directly access these buffers. Instead, it redirects any data request to the \emph{working} buffer which is located in the volatile memory (SRAM) has a lower latency and energy cost to access than the device's FRAM. It populates working buffer with the privatized pages from non-volatile memory. When a coalesced task completes, the VMM ensures that updated pages are committed to main memory and visible to subsequently executed tasks. If the power interrupts a task, the VMM ensures that the task sees consistent memory state when it restarts its execution. The VMM ensures consistency even if a task or a sequence of tasks include WAR dependences that could compromise consistency~\cite{ratchet,dino}.

@@

The memory manager is forced to swap out a dirty page from the \texttt{working} buffer
when a task accesses a page that is not in the working buffer, and there is no
free page in the working buffer (i.e., a page fault). On a page fault, \sys
moves the page to a direct\hyp{}mapped non-volatile \texttt{\underline{shadow}}
page buffer. \\

>>>>

\sys's {\em virtual memory manager} (VMM) abstracts the physical address space of the non-volatile memory (FRAM) and divides it into \texttt{\underline{private}} and \texttt{\underline{shadow}} (underlined locations are non-volatile) buffers. Each buffer is divided into pages. The VMM prohibits applications from directly access these buffers. Instead, it redirects any request to the \texttt{working} buffer located in the volatile memory (SRAM), which has a lower latency and energy cost to access than FRAM. It populates \texttt{working} buffer with the privatized pages from non-volatile memory. When a coalesced task completes, the VMM ensures that updated pages are committed to main memory and visible to subsequently executed tasks. If the power interrupts a task, the VMM ensures the consistency of the data by relying on its \texttt{\underline{private}} buffer. The VMM ensures consistency even if a task or a sequence of tasks include WAR dependences that could compromise consistency~\cite{ratchet,dino}.

@@

The VMM is forced to swap out a dirty page from the \texttt{working} buffer
when a task requests a page that is not in the \texttt{working} buffer, and there is no
free page in the working buffer (i.e., a page fault). On a page fault, the VMM
moves the page to the direct\hyp{}mapped non-volatile \texttt{\underline{shadow}} buffer. \\
